---
title: "Import Data (Bonus)"
output: html_notebook
---

```{r setup}
library(tidyverse)
```

## Your Turn 1

Find nimbus.csv on your server or computer. Then read it into an object. Then view the results.

```{r}

```

## The hole in the ozone layer

```{r}
nimbus <- read_csv("nimbus.csv", na = ".", 
  col_types = list(ozone = col_double()))

library(viridis)
world <- map_data(map = "world")
nimbus %>% 
  ggplot() +
    geom_point(aes(longitude, latitude, color = ozone)) +
    geom_path(aes(long, lat, group = group), data = world) +
    coord_map("ortho", orientation=c(-90, 0, 0)) +
    scale_color_viridis(option = "A")
```

***

# Take Aways

The readr package provides efficient functions for reading and saving common flat file data formats.

Consider these packages for other types of data:

Package  | Reads
-------- | -----
haven    | SPSS, Stata, and SAS files
readxl   | excel files (.xls, .xlsx)
jsonlite | json
xml2     | xml
httr     | web API's
rvest    | web pages (web scraping)
DBI      | databases
sparklyr | data loaded into spark
